Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-09-24 secondPaper/accordionComplexSurfaces.tex
minor mistakes

\begin{definition}
\label{def:slalom}
A \defn{$\dissection\dual$-slalom} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a$ of~$\dissection$ contained in two faces~$f,g$ of~$\dissection$, the marked points~$f\dual$ and~$g\dual$ lie on opposite sides of~$\alpha$ in the union of~$f$ and~$g$ glued along~$a$.
Here, we consider that~$f\dual$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f\dual$.
By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms that are considered external.
If we were working on the universal cover of the surface, the~$\dissection$-accordion associated to a puncture would be the infinite line crossing all (infinitely many) arcs attached to the puncture.
\end{definition}

>>>>

\begin{definition}
\label{def:slalom}
A \defn{$\dissection\dual$-slalom} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that, whenever~$\alpha$ crosses an edge~$a\dual$ of~$\dissection\dual$ contained in two faces~$f\dual, g\dual$ of~$\dissection\dual$, the marked points~$f$ and~$g$ lie on opposite sides of~$\alpha$ in the union of~$f\dual$ and~$g\dual$ glued along~$a\dual$.
Here, we consider that~$f$ lies on the right (resp.~left) of~$\alpha$ when~$\alpha$ circles clockwise (resp.~counterclockwise) around~$f$.
By convention, we also consider that the punctures of~$V$ are $\dissection\dual$-slaloms that are considered external.
If we were working on the universal cover of the surface, the~$\dissection\dual$-slalom associated to a puncture would be an infinite line never crossing any arc of~$\dissection\dual$.
\end{definition}
